Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates

### 2017-11-13 manuscript-md/03_results.Rmd
Fix results plots
Add equation annotation to sample size plot.

Use unaltered means (instead of adjusted plotting data) for sample size
model.

Fix limits on Rdarea in means plot.

plot_dat <- means_dat %>%
  mutate(
    #too_few = sample_size < 2,
    #mu_hi = if_else(too_few, NA_real_, mu_hi),
    #mu_lo = if_else(too_few, NA_real_, mu_lo),
    #mu_mean = if_else(too_few, NA_real_, mu_mean),
    irrelevant = grepl("Vcmax|Jmax", param) & pft == "C4G",
    mu_hi = if_else(irrelevant, NA_real_, mu_hi),
    mu_lo = if_else(irrelevant, NA_real_, mu_lo),
    mu_mean = if_else(irrelevant, NA_real_, mu_mean),
    ## TODO: Fix these in the prior and re-run
    mu_hi = pclip(param, "Vcmax_mass", mu_hi, 1.5),
    mu_hi = pclip(param, "Vcmax_area", mu_hi, 100),
    mu_hi = pclip(param, "Jmax_mass", mu_hi, 1.8),
    mu_hi = pclip(param, "Jmax_area", mu_hi, 150),
    mu_mean = pclip(param, "Jmax_area", mu_mean, 150),
    mu_hi = pclip(param, "Rdmass", mu_hi, 0.03),
    mu_hi = pclip(param, "Rdarea", mu_hi, 1.7),
    mu_mean = pclip(param, "Rdarea", mu_mean, 1.7),
    mu_lo = pclip(param, "Rdarea", mu_lo, 0.5, FALSE),
    mu_hi = pclip(param, "Parea", mu_hi, 0.285),
    #mu_lo = pclip(param, "Jmax_area", mu_lo, 40, FALSE),
    param = forcats::lvls_revalue(param, param_fancy_chr[both_params])
  )

@@

```{r "civssamplesize", fig.width=4.4, fig.height=3, fig.cap='(ref:sscap)'}
## Relative uncertainty
cv_dat <- plot_dat %>%
  mutate(
    cv = abs((mu_hi - mu_lo) / mu_mean)
  ) %>%
  filter(sample_size > 3)

@@

@@

relative_ci <- ggplot(cv_dat) +
  aes(x = sample_size, y = cv, color = model_type) +
  geom_point(size = 0.5) +
  geom_line(data = cv_pred) +
  scale_x_continuous(trans = "log10") +
  coord_cartesian(xlim = x_lims, ylim = y_lims) +
  xlab("Sample size") +
  ylab("Relative width of 95% CI") +
  scale_color_brewer(type = "qual", palette = 2) +
  guides(color = guide_legend(title = "Model type")) +
  theme_bw() +
  theme(
    legend.position = c(0.85, 0.75),
    panel.grid = element_blank()
  )
relative_ci
```

@@

stickplot_pairs(
  #mu_global_lower = dat_list$hier_mass$mu_global,
  #Sigma_global_lower = dat_list$hier_mass$Sigma_global,
  mu_global_lower = dat_list$multi_mass$mu,
  Sigma_global_lower = dat_list$multi_mass$Sigma,
  mu_group_lower = dat_list$hier_mass$mu_group,
  Sigma_group_lower = dat_list$hier_mass$Sigma_group,
  vars_lower = mass_params,
  group_names = pft2abbr[-1],
  vars_label = param_labels,
  unlog_axes = TRUE,
  #mu_global_upper = dat_list$hier_area$mu_global,
  #Sigma_global_upper = dat_list$hier_area$Sigma_global,
  mu_global_upper = dat_list$multi_area$mu,
  Sigma_global_upper = dat_list$multi_area$Sigma,
  mu_group_upper = dat_list$hier_area$mu_group,
  Sigma_group_upper = dat_list$hier_area$Sigma_group,
  vars_upper = area_params,
  col_group = pft_colors,
  cex_g = 1.2,
  lwd_g = 1,
  lty_g = 1,
  lwd_s = 1.3,
  par_plot = list(oma = c(0, 5, 3, 5), cex = 0.4),
  par_legplot = list(mar = c(0, 0, 0, 0)),
  par_legend = list(ncol = 5, x = "center", cex = 0.6)
)
mtext("Mass-normalized", side = 2, cex = 0.7, line = 3)
mtext("Area-normalized", side = 4, cex = 0.7, line = 1)
```

@@

```{r boxprep}
hier_mass_file <- "../output/hier.mass.clm45.NA.2017-11-09-1749.rds"
hier_area_file <- "../output/hier.area.clm45.NA.2017-11-10-0937.rds"
multi_mass_file <- "../output/multi.mass.clm45.NA.2017-11-09-1733.rds"
multi_area_file <- "../output/multi.area.clm45.NA.2017-11-09-1741.rds"

>>>>

plot_dat <- means_dat %>%
  mutate(
    #too_few = sample_size < 2,
    #mu_hi = if_else(too_few, NA_real_, mu_hi),
    #mu_lo = if_else(too_few, NA_real_, mu_lo),
    #mu_mean = if_else(too_few, NA_real_, mu_mean),
    irrelevant = grepl("Vcmax|Jmax", param) & pft == "C4G",
    mu_hi = if_else(irrelevant, NA_real_, mu_hi),
    mu_lo = if_else(irrelevant, NA_real_, mu_lo),
    mu_mean = if_else(irrelevant, NA_real_, mu_mean),
    ## TODO: Fix these in the prior and re-run
    mu_hi = pclip(param, "Vcmax_mass", mu_hi, 1.5),
    mu_hi = pclip(param, "Vcmax_area", mu_hi, 100),
    mu_hi = pclip(param, "Jmax_mass", mu_hi, 1.8),
    mu_hi = pclip(param, "Jmax_area", mu_hi, 150),
    mu_mean = pclip(param, "Jmax_area", mu_mean, 150),
    mu_hi = pclip(param, "Rdmass", mu_hi, 0.03),
    mu_hi = pclip(param, "Rdarea", mu_hi, 0.0035),
    mu_mean = pclip(param, "Rdarea", mu_mean, 0.0035),
    mu_lo = pclip(param, "Rdarea", mu_lo, 0.0035),
    mu_hi = pclip(param, "Parea", mu_hi, 0.285),
    #mu_lo = pclip(param, "Jmax_area", mu_lo, 40, FALSE),
    param = forcats::lvls_revalue(param, param_fancy_chr[both_params])
  )

@@

```{r "civssamplesize", fig.width=4.4, fig.height=3, fig.cap='(ref:sscap)'}
## Relative uncertainty
cv_dat <- means_dat %>%
  mutate(
    cv = abs((mu_hi - mu_lo) / mu_mean)
  ) %>%
  filter(sample_size > 1)

@@

cv_coef <- cv_mod %>%
  mutate(
    coef = map(cvfit, broom::tidy)
  ) %>%
  unnest(coef) %>%
  select(model_type, term, estimate) %>%
  spread(term, estimate) %>%
  "names<-"(c("model_type", "intercept", "slope")) %>%
  mutate(
    eqn = sprintf("'%s: '~log[10](y) == %0.2f - %0.2f~log[10](x)", model_type, intercept, abs(slope))
  )

@@

relative_ci <- ggplot(cv_dat) +
  aes(x = sample_size, y = cv, color = model_type) +
  geom_point(size = 0.5) +
  geom_line(data = cv_pred) +
  annotate("text", x = rep(2500, 3), y = c(1.4, 1.25, 1.1), 
           label = cv_coef$eqn, parse = TRUE, 
           size = 2, vjust = "right") +
  scale_x_continuous(trans = "log10") +
  coord_cartesian(xlim = x_lims, ylim = y_lims) +
  xlab("Sample size") +
  ylab("Relative width of 95% CI") +
  scale_color_brewer(type = "qual", palette = 2) +
  guides(color = guide_legend(title = "Model type")) +
  theme_bw() +
  theme(
    legend.position = c(0.85, 0.75),
    panel.grid = element_blank()
  )
relative_ci
```

@@

stickplot_pairs(
  #mu_global_lower = dat_list$hier_mass$mu_global,
  #Sigma_global_lower = dat_list$hier_mass$Sigma_global,
  mu_global_lower = dat_list$multi_mass$mu,
  Sigma_global_lower = dat_list$multi_mass$Sigma,
  mu_group_lower = dat_list$hier_mass$mu_group,
  Sigma_group_lower = dat_list$hier_mass$Sigma_group,
  vars_lower = mass_params,
  group_names = pft2abbr[-1],
  vars_label = param_labels,
  unlog_axes = TRUE,
  #mu_global_upper = dat_list$hier_area$mu_global,
  #Sigma_global_upper = dat_list$hier_area$Sigma_global,
  mu_global_upper = dat_list$multi_area$mu,
  Sigma_global_upper = dat_list$multi_area$Sigma,
  mu_group_upper = dat_list$hier_area$mu_group,
  Sigma_group_upper = dat_list$hier_area$Sigma_group,
  vars_upper = area_params,
  col_group = pft_colors,
  cex_g = 1.2,
  lwd_g = 1,
  lty_g = 1,
  lwd_s = 1.3,
  par_plot = list(oma = c(0, 5, 3, 5), cex = 0.4),
  par_legplot = list(mar = c(0, 0, 0, 0)),
  par_legend = list(ncol = 5, x = "center", cex = 0.6),
  reorder_legend = TRUE
)
mtext("Mass-normalized", side = 2, cex = 0.7, line = 3)
mtext("Area-normalized", side = 4, cex = 0.7, line = 1)
```

@@

```{r boxprep}
hier_mass_file <- "../output/hier.mass.clm45.NA.2017-11-13-1250.rds"
hier_area_file <- "../output/hier.area.clm45.NA.2017-11-13-1312.rds"
multi_mass_file <- "../output/multi.mass.clm45.NA.2017-11-13-1231.rds"
multi_area_file <- "../output/multi.area.clm45.NA.2017-11-13-1245.rds"
